---
title: "MATH2270 Assignment 2"
subtitle: Visualising Open Data
output:
  html_document:
    df_print: paged
---

<style> body { text-align: justify} </style>

## Student Details
* Alistair Grevis-James (s3644119)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


https://www.kaggle.com/zhangjuefei/birds-bones-and-living-habits

About

According to their living environments and living habits, birds are classified into different ecological groups. There are 8 ecological groups of birds:

* Swimming Birds
* Wading Birds
* Terrestrial Birds
* Raptors
* Scansorial Birds
* Singing Birds
* Cursorial Birds (not included in dataset)
* Marine Birds (not included in dataset)

First 6 groups are main and are covered by this dataset.

There are 420 birds contained in this dataset. Each bird is represented by 10 measurements (features):

* Length and Diameter of Humerus
* Length and Diameter of Ulna
* Length and Diameter of Femur
* Length and Diameter of Tibiotarsus
* Length and Diameter of Tarsometatarsus

```{r message=FALSE, warning=FALSE}
# Load your packages
library(tidyr)
library(dplyr)
library(knitr)
library(GGally)
library(ggplot2)
library(ggridges)
```

## Data

```{r warning=FALSE}
# Load your data and prepare for visualisation
birdDS <- read.csv("bird.csv")
```

## Exploring the Data

```{r warning=FALSE}
# Load your data and prepare for visualisation
head(birdDS)
```

```{r warning=FALSE}
colnames(birdDS)
```

```{r warning=FALSE}
colNamesFull <- c("ID", "HumerusLength", "HumerusDiameter", "UlnaLength", "UlnaDiameter",
                  "FemurLength", "FemurDiameter", "TibiotarusLength", "TibiotarusDiameter",
                  "TarsometatarusLength", "TarsometatarusDiameter", "EcologicalBirdType")
```


```{r warning=FALSE}
# Load your data and prepare for visualisation
summary(birdDS)
```

```{r warning=FALSE}
# Load your data and prepare for visualisation
str(birdDS)
```

```{r warning=FALSE}
# Load your data and prepare for visualisation
head(birdDS)
```

```{r warning=FALSE}
# Check the species ID
unique(birdDS$type)
```

#### Determine the mean values

```{r warning=FALSE}
# SW - Swimming Birds
SWbirds <- subset(birdDS, birdDS$type == "SW") # SW - Swimming Birds
Wbirds <- subset(birdDS, birdDS$type == "W") # W - Wading Birds
Tbirds <- subset(birdDS, birdDS$type == "T") # T - Terrestrial Birds
Rbirds <- subset(birdDS, birdDS$type == "R") # R - Raptors
Pbirds <- subset(birdDS, birdDS$type == "P") # P - Scansorial Birds
SObirds <- subset(birdDS, birdDS$type == "SO") # SO - Singing Birds
```



```{r warning=FALSE}
# Filling NA - Rbirds
Wbirds$feml[is.na(Wbirds$feml)] <- mean(Wbirds$feml, na.rm = TRUE)
Wbirds$femw[is.na(Wbirds$femw)] <- mean(Wbirds$femw, na.rm = TRUE)
```

```{r warning=FALSE}
# Filling NA - Rbirds
Rbirds$ulnal[is.na(Rbirds$ulnal)] <- mean(Rbirds$ulnal, na.rm = TRUE)
Rbirds$ulnaw[is.na(Rbirds$ulnaw)] <- mean(Rbirds$ulnaw, na.rm = TRUE)
Rbirds$tarl[is.na(Rbirds$tarl)] <- mean(Rbirds$tarl, na.rm = TRUE)
Rbirds$tarw[is.na(Rbirds$tarw)] <- mean(Rbirds$tarw, na.rm = TRUE)
```

```{r warning=FALSE}
# Filling NA - SObirds
SObirds$huml[is.na(SObirds$huml)] <- mean(SObirds$huml, na.rm = TRUE)
SObirds$humw[is.na(SObirds$humw)] <- mean(SObirds$humw, na.rm = TRUE)
SObirds$ulnal[is.na(SObirds$ulnal)] <- mean(SObirds$ulnal, na.rm = TRUE)
SObirds$ulnaw[is.na(SObirds$ulnaw)] <- mean(SObirds$ulnaw, na.rm = TRUE)
SObirds$feml[is.na(SObirds$feml)] <- mean(SObirds$feml, na.rm = TRUE)
SObirds$tibl[is.na(SObirds$tibl)] <- mean(SObirds$tibl, na.rm = TRUE)
SObirds$tibw[is.na(SObirds$tibw)] <- mean(SObirds$tibw, na.rm = TRUE)
```

```{r warning=FALSE}
birdDS_clean <- rbind(SWbirds, Wbirds, Tbirds, Rbirds, Pbirds, SObirds)
```

```{r warning=FALSE}
summary(birdDS_clean)
```

## Visualisation

```{r warning=FALSE}
colnames(birdDS_clean)
```

```{r warning=FALSE}
allMeasurements <- c("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw")
lengthMeasurements <- c("huml", "ulnal", "feml",  "tibl",  "tarl")
widthMeasurements <- c("humw", "ulnaw",  "femw", "tibw", "tarw")
```


```{r warning=FALSE}
test_reorder <- birdDS_clean[,c(12,2,3,4,5,6,7,8,9,10,11,1)]
```

```{r warning=FALSE}
test <- birdDS_clean %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "id", value = "measurement")
```

```{r warning=FALSE}
SWbirdsLong <- SWbirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
SWbirdsLong$id <- 'SW'
WbirdsLong <- Wbirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
WbirdsLong$id <- 'W'
TbirdsLong <- Tbirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
TbirdsLong$id <- 'T'
RbirdsLong <- Rbirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
RbirdsLong$id <- 'R'
PbirdsLong <- Pbirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
PbirdsLong$id <- 'P'
SObirdsLong <- SObirds %>% gather("huml", "humw", "ulnal", "ulnaw", "feml",  "femw",  "tibl",  "tibw",  "tarl",  "tarw", 
                   key = "type", value = "measurement")
SObirdsLong$id <- 'SO'
```

```{r warning=FALSE}
birdDS_Long <- rbind(SWbirdsLong, WbirdsLong, TbirdsLong, RbirdsLong, PbirdsLong, SObirdsLong)
```

```{r warning=FALSE}
summary(birdDS_Long)
```

```{r warning=FALSE}
colnames(birdDS_Long) <- c("birdType", "bone", "measurement")
```


```{r warning=FALSE}
birdDS_Long$measurementType <- sapply(strsplit(as.character(birdDS_Long$bone), ""), tail, 1)
birdDS_Long$boneAlone = substr(birdDS_Long$bone,1,nchar(birdDS_Long$bone)-1)
```


```{r warning=FALSE}
birdDS_Long$boneAlone <- factor(birdDS_Long$boneAlone)
levels(birdDS_Long$boneAlone) <- c("Femur", "Humerus", "Tarsometatarus", "Tibiotarsus", "Ulna")
levels(birdDS_Long$boneAlone)
```


```{r fig.height=18, fig.width=32, warning=FALSE, message=FALSE}
png('birds.png', units="in", width=32, height=18, res=300)
birdsPlot <- ggplot(data = birdDS_Long, 
                    aes(x=birdDS_Long$measurement, 
                        y = birdType, 
                        fill = measurementType))
birdsPlot <- birdsPlot + geom_density_ridges2(scale = 0.9, alpha=0.7, colour = 'white', size = 0.5) +
  labs(y = NULL, x = "Measurement (mm)", 
       title = "Bird Bone Measurements",
       subtitle = "Alistair Grevis-James s3644119",
       caption="Source: kaggle.com/zhangjuefei/birds-bones-and-living-habits.") +
  theme(plot.title=element_text(size=62, 
                                    face="bold", 
                                    family="American Typewriter",
                                    color="grey30"),
        plot.subtitle=element_text(size=30, 
                                    family="American Typewriter",
                                    color="grey30"),
        plot.caption = element_text(size=24, 
                                   color="grey30"),
        axis.title.x=element_text(vjust=0,
                                  face = "bold",
                                  family="American Typewriter",
                                  size=30),
        axis.text.y = element_text(vjust = 0, 
                                   family="American Typewriter",
                                   size = 30),
        axis.text.x = element_text(size = 20,
                                   family="American Typewriter"),
        strip.text.x = element_text(size = 30,
                                   family="American Typewriter"),
        legend.text = element_text(size=24)) +
  guides(fill = guide_legend(keywidth = 2.5, keyheight = 2.5)) +
  scale_x_continuous(expand = c(0.01, 0), breaks = c(0, 25, 50, 75, 100, 125)) +
  coord_cartesian(xlim = c(0, 150)) +  
  scale_y_discrete(expand = c(0.01, 0), labels=c("Scansorial Birds", "Raptors", 
                                                   "Song Birds", "Swimming Birds", 
                                                   "Terrestrial Birds", "Wading Birds")) + 
  facet_grid(.~boneAlone) +
  theme(legend.title = element_blank()) +
  theme(legend.position = c(0.95, 0.09)) +
  scale_fill_manual(values = c("#ff7f00", "#377eb8"), labels=c("Length", "Width"))

birdsPlot
dev.off()
```

```{r fig.height=18, fig.width=32, warning=FALSE, message=FALSE, fig.cap="The figure shows a series of faceted density plots of bird bone measurements. The measurements are of either length in orange or diameter (width) in blue – all measurements are in mm. The plots are faceted by bone type, and each row represents a type of bird. The visualisation is highly effective at showing the relation between length and diameter of a particular bone, within a particular bird type. The visualisation also allows for distribution comparisons between bird groups and for distribution comparisons between bone types. Starting in the top left-hand corner, we see for example that femur measurements of wading birds are very widely distributed. If we look to terrestrial birds, we see the femur length and width are extremely highly correlated. This correlation can then be compared with the other bones measured."}
birdsPlot
```

